Algomusicology, ????, Profit

### 2016-05-29 paper.tex
Break up double example.
Fix overspills.

  (->>
    (phrase [3/3  3/3  2/3  1/3  3/3]
            [  0    0    0    1    2])
    (times 2))
\end{verbatim}

@@

We can calculate the ratio between the literal notes of the song and the above description.
The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
having to paste in the entire expression.

@@

There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to `Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.

>>>>

\end{verbatim}

And alternatively:

\begin{verbatim}
  (->>
    (phrase [3/3  3/3  2/3  1/3  3/3]
            [  0    0    0    1    2])
    (times 2))
\end{verbatim}

@@

We can calculate the ratio between the literal notes of the song and the above description.
The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, without
having to paste in the entire expression.

@@

Nothing in the the \verb|copyright-infringement-song|'s description is in any way related to `Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.
